Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-22 paperDistance/paper.tex
intro text re assumptions

This project is fundamentally a demonstration of concept:
We are only using the ``small'' (relative to the expected final \gaia\ data set)
\tgas\ Catalog.
We are performing only an approximation to full Bayesian hierarchical inference.
We have to use photometry that is ground-based, rather than the full-precision,
space-based photometry that the \gaia\ Mission will deliver.
However, as we show below, we get very good results.
It is promising that we will be able to obtain similar or even better results
in later \gaia\ data releases, and eventually put distances on $>10^9$
\gaia\ stars using photometric distance methodologies but without any
commitment to---or even use of---physical models of stars.

>>>>

On a different tack, there has been some discussion in the literature
about how to use a parallax responsibly to infer a distance (CITE TRI+CBJ).
These papers use the \gaia\ measurement to construct a parallax likelihood,
and combine this with a distance prior.
While this is sensible and correct, all present methods proposed along
these lines build in informative (and known-to-be-wrong) assumptions
about the line-of-sight distance distribution to \gaia\ stars.
That is, they build in strong and informative assumptions about the Milky
Way.
The methodology presented in this paper makes exceedingly weak assumptions
about the Milky Way, and similarly weak assumptions about the properties of
stars.
The strongest new assumption made in this work is that for every star
in \tgas, there are other, photometrically (and bolometrically)
similar stars.
That is a much weaker assumption than has been made in other Bayesian
distance estimations.

This project is fundamentally a demonstration of concept:
We are only using the ``small'' (relative to the expected final \gaia\ data set)
\tgas\ Catalog.
We are performing only an approximation to full Bayesian hierarchical inference.
We have to use photometry that is ground-based, rather than the full-precision,
space-based photometry that the \gaia\ Mission will deliver.
However, as we show below, we get very good results.
It is promising that we will be able to obtain similar or even better results
in later \gaia\ data releases, and eventually put distances on $>10^9$
\gaia\ stars using photometric distance methodologies but without any
commitment to---or even use of---physical models of stars or the Milky Way.
